Peer Assessment 1
=================

*This is my first R markdown and it is for the peer assessment 1 for course Reproducible data*

###1.Loading and preprocessing the data
```{r Read the explore the data, cache=TRUE}
setwd("~/GitHub/RepData_PeerAssessment1");
actData = read.csv("activity.csv");
actData[,2]=as.character(actData[,2]);
actData[,2]=as.Date(actData[,2],"%Y-%m-%d");
summary(actData);
```

###2.Mean total number of steps taken per day
```{r cal the mean per day, cache=TRUE}
library(plyr);
dt=na.omit(actData);
stepsAnly=ddply(dt,~date,summarize,meanStep=mean(steps),totalStep=sum(steps));
stepsMedian=median(stepsAnly$totalStep);
stepsMean = mean(stepsAnly$totalStep);
hist(stepsAnly$totalStep,breaks = 10,main="Histogram of total steps per day",
     xlab="Total Steps");
```

The mean of total number of steps taken per day is `r stepsMean` steps. And the median of total number of steps taken per day is `r stepsMedian` steps.

###3.Average daily activities
```{r ,cache=TRUE}
stepPattern = ddply(dt,~interval,summarize,pattern=mean(steps));
plot(stepPattern$interval,stepPattern$pattern,type="l",main="Daily activity 
     pattern",xlab="Time Interval",ylab="Average Steps");
stepMaxInterval = stepPattern[which.max(stepPattern[,2]),1];
hour=floor(stepMaxInterval/100);
minute=stepMaxInterval%%100;
```

The maximum number of steps occurs at `r hour`:`r minute`.

###4. Imputing missing values
```{r,cache=TRUE}
nNA = sum(is.na(actData[,1]));
dtf = actData;
dtf$steps[is.na(dtf$steps)]<-0;
stepsAnly=ddply(dtf,~date,summarize,meanStep=mean(steps),totalStep=sum(steps));
stepsMedian=median(stepsAnly$totalStep);
stepsMean = mean(stepsAnly$totalStep);
hist(stepsAnly$totalStep,breaks = 10,main="Histogram of total steps per day with NA filled",
     xlab="Total Steps");
```

The mean of total number of steps taken per day is `r stepsMean` steps. And the median of total number of steps taken per day is `r stepsMedian` steps.

After filling the NA with 0, the frequecy of 0 increases dramatically in the histogram. Therefore, the value of mean and median drop slightly because the value pool contains more 0 now. 

###5. Activity patterns between weekdays and weekends
```{r,cache=TRUE}
dtf$TimeOfWeek<-ifelse(weekdays(dtf$date,TRUE)=="“y"|weekdays(dtf$date,TRUE)=="“ú",
                       "weekends","weekdays")
stepPatternWD = ddply(dtf[dtf$TimeOfWeek=="weekdays",],~interval,summarize,pattern=mean(steps));
stepPatternWE = ddply(dtf[dtf$TimeOfWeek=="weekends",],~interval,summarize,pattern=mean(steps));
par(mfrow = c(2,1), mar=c(4,4,2,1));
plot(stepPatternWD$interval,stepPatternWD$pattern,type="l",ylim=c(0,200),
     xlab="Interval",ylab="Number of Steps",main="weekdays");
plot(stepPatternWE$interval,stepPatternWE$pattern,type="l",ylim=c(0,200),
     xlab="Interval",ylab="Number of Steps",main="weekends");
```
